Conjure: Summoning Proxies from Unused Address Space

### 2019-09-26 paper/figures.tex
figure caption

\newcommand{\FigOverview}{
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/dark-decoy-flow2.png}
    \caption{\textbf{\scheme Operations}\,---\,\rm%
        A \scheme session is constructed in two pieces. First a client registers by sending a tls connection
        to the Decoy host (see Figure 2c) with a steganographically tagged payload.
        This registration contains the true address that the client would like to connect to and a seed 
        which the \scheme station uses to derive the Phantom IP address for the session(green dashed flow). 
        Second The client derives the same 
        Phantom IP address and connects directly to it using the proxy protocol (e.g. OSSH) that they specified in
        their registration (purple dotted flow). The station identifies registered packets by source IP, destination IP,
        and destination port (client IP, phantom IP, and phantom port respectively). The traffic is passed 
        to a proxy server handling the specific proxy specified by the client then redirected to the 
        covert address that the client indicated in their registration. 
        \\\hspace{\textwidth}
        Secrets for the individual proxy services are shared out of band or derived from the shared secret 
        between the client and the station such that an adversary attempting to probe a connection will be
        unable to connect to the proxy service. 
    }
    \label{fig:overview}
\end{figure}
}

>>>>

\newcommand{\FigOverview}{
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/dark-decoy-flow2.png}
    \caption{\textbf{\scheme Operations}\,---\,\rm%
        A \scheme session is constructed in two pieces. First a client registers by sending a TLS connection
        to the decoy host (see Figure 2c) with a steganographically tagged payload.
        This registration contains the true ``covert'' address that the client would like to connect to and a seed 
        which the \scheme station uses to derive the Phantom IP address for the session (green dashed flow). 
        Second, the client derives the same 
        Phantom IP address and connects directly to it using the proxy protocol (e.g. OSSH) specified in
        the registration (purple dotted flow). The station identifies registered packets by source IP, destination IP,
        and destination port (client IP, phantom IP and port respectively). The traffic is passed 
        to a proxy server handling the specific proxy protocol, which ultimately proxies traffic to
        the covert address.
        \\\hspace{\textwidth}
        Secrets for the individual application proxy service are shared out of band or derived from the secret seed shared
        between client and station during registration, preventing an adversary from being
        able to successfully connect to the application in follow up probes.
    }
    \label{fig:overview}
\end{figure}
}
